---
title: "Common Interests Amongst Users"
output: html_notebook
---

# Problem
Count the subpopulations across datasets. Assume that a subpopulation is a group of users sharing a common interest (ex: Basketball, Food). Output the percentage of overlapping interests for two posters along with those poster's IDs. Calculate the percentage from the number of poster's interests. The poster column in the dataset refers to the user that posted the comment.

## Inputs

```{r R-Inputs}

data_loc <- file.path("~/Data Science/Exercises/Data", "facebook_posts.csv")
facebook_posts <- read.csv2(data_loc)
facebook_posts <- facebook_posts %>% mutate(post_date=as.POSIXct(post_date))

```

```{python}
import pandas as pd
import numpy as np

facebook_posts = pd.read_csv("~/Data Science/Exercises/Data/facebook_posts.csv", sep=";")
facebook_posts['post_date'] = pd.to_datetime(facebook_posts['post_date'])
facebook_posts
```

## Expected Output

```{r}
overlap <- c(0.6, 0.6)
poster1 <- c(2, 1)
poster2 <- c(1, 2)
solution <- data.frame(overlap, poster1, poster2)
solution
```


# Solutions


## Python

### My Solution

```{python}
# MY SOLUTION

# Convert post_keywords from str to list

facebook_posts2 = facebook_posts.copy()

facebook_posts2['post_keywords_list'] = facebook_posts2.post_keywords.str[1:-1].str.split(',')

# Explode list to elongate the data
poster_to_interests = facebook_posts2.explode('post_keywords_list')

# Set spam to NA (not an interest)
poster_to_interests.post_keywords_list.loc[poster_to_interests.post_keywords_list == '#spam#'] = pd.NA

# Group by poster and aggregate as a list (not including NAs)
poster_to_interests = poster_to_interests.groupby('poster')['post_keywords_list'].agg(lambda series: list(series.dropna()))

ptif = poster_to_interests.to_frame().reset_index()

# Cross join so we can compare posters and their keywords to each other
ptif = pd.merge(ptif, ptif, how="cross")

# Want a function that will calculate the percentage of overlapping elements between list1 and list2
def overlap(list1, list2):
    combined = list1 + list2
    if len(list1) == 0:
        return 0
    combined_set = set(combined)
    return len(set(list1) & set(list2))/len(list1)
    
a = ['basketball', 'lebron_james', 'nba', 'spaghetti', 'food']
b = ['basketball', 'lakers', 'nba', 'asparagus', 'food']

ptif = ptif.loc[ptif.poster_x != ptif.poster_y]
overlaps = ptif.apply(lambda series: overlap(series['post_keywords_list_x'], series['post_keywords_list_y']), axis=1)

ptif['overlap'] = overlaps

my_result = ptif[['poster_x', 'poster_y', 'overlap']].loc[ptif.overlap > 0]

my_result
```


### stratascratch solution
```{python}

facebook_posts2 = facebook_posts.copy()

facebook_posts2['post_keywords'] = facebook_posts2['post_keywords'].apply(
    lambda x: x[1:-1].split(','))
    
result = facebook_posts2.groupby('poster')['post_keywords'].sum().reset_index()


result['constant'] = [1] * result.shape[0]

result = result.merge(result, on='constant')

result = result[result['poster_x'] != result['poster_y']]


result['intersection'] = [[]] * result.shape[0]

result['total'] = result['post_keywords_x'].apply(lambda x: len(x))

for i, r in result.iterrows():
    result['intersection'].loc[i] = len(
        list(set(r['post_keywords_y']) & set(r['post_keywords_x'])))


result['overlap'] = result['intersection'] / result['total']


result = result[['poster_x', 'poster_y', 'overlap']]
result = result[result.overlap > 0]

result

```

## R

### My solution

```{r}
library(tidyverse)
library(stringr)

facebook_posts2 <- facebook_posts %>% mutate(post_keywords_list = str_split(str_sub(post_keywords, 2, -2), ","))

poster_to_interests <- facebook_posts2 %>% 
  group_by(poster) %>% 
  reframe(interests =unlist(post_keywords_list, recursive = FALSE)) %>% 
  distinct(.keep_all = TRUE)  %>% 
  mutate(interests = if_else(interests=="#spam#", NA, interests)) %>% 
  group_by(poster) %>% 
  summarize(interests=list(unique(interests[!is.na(interests)])))

my_results <- poster_to_interests %>% cross_join(poster_to_interests) %>% 
  filter(poster.x != poster.y) %>% 
  rowwise() %>% 
  mutate(overlap = length(intersect(interests.x, interests.y))/length(interests.x))

my_results$overlap[is.nan(my_results$overlap)] <- 0

my_results %>% select(poster.x, poster.y, overlap) %>% filter(overlap>0)


```
### Their Solution

```{r}

library(tidyverse)
x = facebook_posts%>%
    select(poster, post_keywords)%>%
    mutate(post_keywords = str_extract_all(post_keywords, '[a-z_]+'))%>%
    unnest(post_keywords)

x%>%
    group_by(poster)%>%
    mutate(all_count = n_distinct(post_keywords))%>%
    ungroup()%>%
    inner_join(x, by = 'post_keywords', keep = T)%>%
    filter(poster.x != poster.y) %>%
    group_by(poster.x)%>%
    mutate(intersect_count = n(), overlap = intersect_count/all_count)%>%
    ungroup()%>%
    distinct(poster1 = poster.x, poster2 = poster.y, overlap)


```

## SQL
```{r}
library(odbc)
library(DBI)
library(tidyverse)
conn <- dbConnect(drv = RSQLite::SQLite(),
                  dbname = ":memory:")
dbWriteTable(conn=conn,
             name="facebook_posts",
             value=facebook_posts)
```


### My Solution

```{sql connection=conn}
-- Convert post_keywords into keywords list
WITH keywords(keywords, poster) AS (SELECT REPLACE(REPLACE(post_keywords, ']', ''), '[', ''), poster
                            FROM facebook_posts),
-- Find number of words for each keyword 
     keywordsCount(keywords, word_count, poster) AS (SELECT keywords, 
                                                   (1 + LENGTH(keywords)-LENGTH(REPLACE(keywords, ',', ''))) , poster
                                            FROM keywords),
                                            
     --all_keywords(keywords, rest_word, startPos, counter) AS (SELECT keywords, )
     all_keywords(keywords, rest_word, counter, wc, pos) AS (SELECT keywords, SUBSTRING(keywords, INSTR(keywords, ",")+1), 1, word_count, poster
                                                        FROM keywordsCount
                                                        UNION ALL
                                                        SELECT rest_word, SUBSTRING(rest_word, INSTR(rest_word, ",")+1), counter + 1, wc, pos
                                                        FROM all_keywords, keywordsCount
                                                        WHERE counter < wc ),
     temp(keyword, poster) AS (SELECT CASE WHEN counter=wc THEN keywords
                                               ELSE REPLACE(keywords, ',' || rest_word, '')
                                          END, pos
                                   FROM all_keywords),
                       
     keyword_to_poster AS (SELECT DISTINCT keyword, poster FROM temp),
     
     posters AS (SELECT DISTINCT poster FROM keyword_to_poster),
    
     overlap AS (SELECT p1.poster AS posterx, p2.poster AS postery, (SELECT COUNT(*) FROM (SELECT keyword FROM keyword_to_poster WHERE keyword_to_poster.poster = p1.poster
                                                                                           INTERSECT
                                                                                           SELECT keyword FROM keyword_to_poster WHERE keyword_to_poster.poster = p2.poster)) AS total_overlap
                 FROM posters AS p1, posters AS p2
                 WHERE posterx != postery)

SELECT posterx, postery, CAST(total_overlap AS double)/CAST(total_words AS double) AS overlap  FROM overlap
LEFT JOIN
(SELECT poster, COUNT(keyword) AS total_words FROM keyword_to_poster 
 WHERE keyword != '#spam#'
 GROUP BY poster) AS keywordC
ON posterx = keywordC.poster
WHERE overlap > 0




```


### Their solution
```{sql connection=conn}



```

